### 2010-03-30 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: use \citet instead of re-writing stuffs.
Desc@ICFP: update TODO. Fix a typo.

However, one could, quite rightfully, be worried by the introduction
of equalities in the picture. In a programming context, equalities
haunt us, begging for proofs. Hence, whereas the developer typed a
constructor-constrained data-type, the elimination form will involve
equalities and their proofs. As much as possible, one would rather
avoid suffering from this burden. However, the equalities introduced
here are rather special: they are \emph{equations} constraining
variables to certain terms. Goguen et
al.~\cite{goguen:pattern-matching} have shown, in the context of
dependent pattern matching, how to tame these equations.

@@

Further, we can actually remove these equations altogether. Let us look back
at $\D{Vec}$. We note that the equations are introduced because we are
\emph{storing} the index of the inductive family.  However, \emph{inductive
families need not store their indices}~\cite{brady:index-inductive-families}.
By examining the in coming index, we can apply the \emph{forcing} and
\emph{de-tagging} optimisations to our initial definition of $\D{Vec}$ gives
the following, equivalent definition:

>>>>

However, one could, quite rightfully, be worried by the introduction
of equalities in the picture. In a programming context, equalities
haunt us, begging for proofs. Hence, whereas the developer typed a
constructor-constrained data-type, the elimination form will involve
equalities and their proofs. As much as possible, one would rather
avoid suffering from this burden. However, the equalities introduced
here are rather special: they are \emph{equations} constraining
variables to certain terms. \citet{goguen:pattern-matching} have
shown, in the context of dependent pattern matching, how to tame these
equations.

@@

Further, we can actually remove these equations altogether. Let us
look back at $\D{Vec}$. We note that the equations are introduced
because we are \emph{storing} the index of the inductive family.
However, \emph{inductive families need not store their
  indices}~\cite{brady:index-inductive-families}.  By examining the
incoming index, we can apply the \emph{forcing} and \emph{de-tagging}
optimisations to our initial definition of $\D{Vec}$ gives the
following, equivalent definition:
